Impact of Demographics and Skills of the Observer on Visual Statistical Inference

### 2013-05-27 sociology_paper.tex
demographic information added

@@

Because of its convenience it is getting popular for scientific research study. In comparison with a lab study \cite{suri:2010} perform the same study using MTurk and demonstrate that their study results are as good as the lab study results even though MTurk study required less time, cost and provided more convenience. \cite{majumder:2012} recruited people from MTurk for their simulation study in estimating the power of visual statistical inference. They have done numerous pilot studies in lab before doing actual MTurk study and found similar results. \cite{mason:2012} explains various features of MTurk and describes how it can be used as part of human behavioral study.

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{demographic_info.pdf} 
   \caption{Countrywise distribution of age levels of the MTurk workers participating the experiments.}
   \label{fig:age_study}
\end{figure}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{learning_trend.pdf} 
   \caption{Mean absolute residuals vs attempt obtained by adjusting for lineup and subject specific variation. For experiment 5, we see a downward trend which may indicate some learning as attempt progress, but none of the slopes in these three experiments are statistically significant.}
   \label{fig:learning_trend}
\end{figure}

@@

>>>>

%\section{Kodu} Tui ekta chor. Tore kilai.

@@

Because of its convenience it is getting popular for scientific research study. In comparison with a lab study \cite{suri:2010} perform the same study using MTurk and demonstrate that their study results are as good as the lab study results even though MTurk study required less time and cost while provided more convenience. \cite{majumder:2012} recruited people from MTurk for their simulation study in estimating the power of visual statistical inference. They have done numerous pilot studies in lab before doing actual MTurk study and found similar results. \cite{mason:2012} explains various features of MTurk and describes how it can be used as part of human behavioral study.

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6in]{demographic_info.pdf} 
   \caption{Countrywise distribution of age and academic levels of the MTurk workers participating the experiments shows the diversity of the subjects in all the demographic aspect. Almost equal number of male and female subjects participated the online experiments.}
   \label{fig:age_study}
\end{figure}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{learning_trend_time.pdf} 
   \caption{Mean residuals of time taken vs attempt obtained by adjusting for lineup and subject specific variation. For all the experiment the downward slopes indicate that MTurk workers take less time as they progress through their attempts.}
   \label{fig:learning_trend_time}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{learning_trend.pdf} 
   \caption{ Mean residuals of proportion correct vs attempt obtained by adjusting for lineup and subject specific variation. For experiment 5, we see a downward trend which may indicate some learning as attempt progress, but none of the slopes in these three experiments are statistically significant.}
   \label{fig:learning_trend}
\end{figure}

@@

\begin{table}[hbtp]
\caption{Demographic information of the subjects participated the MTurk experiments.}
\centering
\begin{tabular}{rlrrr}
  \hline
 & levels & subsjects & avg\_time & response \\ 
  \hline
Gender & Male & 1348 & 48.51 & 13493 \\ 
   & Female & 991 & 43.75 & 10564 \\ 
\hline
  Education & High school or less & 193 & 37.21 & 2241 \\ 
   & Some under graduate courses & 418 & 42.84 & 4070 \\ 
   & Under graduate degree & 584 & 44.29 & 5775 \\ 
   & Some graduate courses & 245 & 43.43 & 2460 \\ 
   & Graduate degree & 902 & 52.18 & 9511 \\ 
\hline
  Age & 18-25 & 740 & 42.97 & 7311 \\ 
   & 26-30 & 547 & 46.27 & 5585 \\ 
   & 31-35 & 376 & 44.27 & 3923 \\ 
   & 36-40 & 257 & 55.03 & 2714 \\ 
   & 41-45 & 141 & 43.90 & 1519 \\ 
   & 46-50 &  95 & 49.29 & 1003 \\ 
   & 51-55 &  83 & 48.67 & 867 \\ 
   & 56-60 &  64 & 59.73 & 678 \\ 
   & above 60 &  38 & 48.67 & 457 \\ 
   \hline
\end{tabular}\label{tbl:demographics}
\end{table}
